\cvsection{Work experience}

% CONSTRUCTOR
\cvevent{Machine Learning Engineer}
{\href{https://constructor.io/}{Constructor.io Corporation}}{June 2023 -- November 2023}{Remote}
\begin{itemize}
\item \textbf{In the Attribute Enrichment Team.} Enhanced the quality of existing methods that enrich product descriptions. Developed and productionized a metrics pipeline for these methods.
\item \textbf{In the Search Team.} Researched thresholding methods for retrieval.
\end{itemize}

\divider

% NEW YORKER
\cvevent{Staff Data Scientist / Team Lead}
{\href{https://www.newyorker.de/}{NewYorker GmbH}}{March 2021 -- June 2023}{Berlin, Germany}
I led a team working on \textbf{vector representation} for the images of the company's product catalog.
I was responsible for research and development and also
communicated with other teams and stakeholders to identify the best use of
our model. Ultimately, I facilitated its exposure as an internal API. 

\begin{itemize}
\item Thanks to this API our colleagues from other DS projects boosted their business metrics. 
\item I also released the training pipeline as an open-source \href{https://github.com/OML-Team/open-metric-learning}{\underline{library}} and promoted
it at 
\href{https://drive.google.com/drive/folders/1uHmLU8vMrMVMFodt36u0uXAgYjG_3D30?usp=share_link}{\underline{meetups}}
to improve our employer branding. 
\end{itemize}

\divider

% NEUROMATION
\cvevent{Applied Data Scientist}{\href{https://neu.ro/}{Neuromation Inc.}}{March 2018 -- October 2020}{}
I completed numerous projects working as a consultant, e.g.:
\begin{itemize}
\item Built a \textbf{Computer Vision} system that saved doctors' time by verifying if a box with surgical tools was correctly completed. The challenge lay in solving the problem without retraining the model for new tools, using a few-shot learning approach.
\item Developed an \textbf{NLP} tool to assist operators in extracting useful information from emails. This involved the entire project lifecycle from client communication and setting up the data labeling process to containerization and deploying the trained model.
\end{itemize}

\divider

% 3RED
\cvevent{Junior Quant Analyst}{\href{https://www.3redpartners.com/}{3Red Trading, LLC}}{June 2016 -- March 2017}{}
Based on statistical anomalies, I recognized traders who used automatic tools so we can predict their actions.
\smallskip
\smallskip
